---
output: github_document
---


<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r setup, echo = FALSE, message = FALSE}
options(width = 100)
Sys.setlocale("LC_COLLATE", "en_US.UTF-8") # ensure common sorting envir
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
ver <- desc::desc_get_version(".")
ver <- paste0("https://img.shields.io/badge/Version-", ver,
              "-success.svg?style=flat&logo=github")
```


# The `stabilityselectr` package

<!-- badges: start -->
![GitHub version](`r ver`)
[![CRAN status](http://www.r-pkg.org/badges/version/stabilityselectr)](https://cran.r-project.org/package=stabilityselectr)
[![R-CMD-check](https://github.com/stufield/stabilityselectr/workflows/R-CMD-check/badge.svg)](https://github.com/stufield/stabilityselectr/actions)
[![](https://cranlogs.r-pkg.org/badges/grand-total/stabilityselectr)](https://cran.r-project.org/package=stabilityselectr)
[![test coverage](https://codecov.io/gh/stufield/stabilityselectr/branch/main/graph/badge.svg)](https://app.codecov.io/gh/stufield/stabilityselectr?branch=main)
[![lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg)](https://choosealicense.com/licenses/mit/)
<!-- badges: end -->




## Overview

The `stabilityselectr` package performs stability selection with a 
variety of kernels provided by the `glmnet` package, and provides 
simple tools for plotting and extracting selected features.
There is additional functionality designed to facilitate
various forms of permutation clustering analyses.


----------------


## Installation

```{r install-git, eval = FALSE}
# current dev version
remotes::install_github("stufield/stabilityselectr")

# or a specific version
remotes::install_github("stufield/stabilityselectr@v0.0.1")
```

----------------


## Usage

To load `stabilityselectr` simply make a call to `library()` as usual:

```{r, eval = FALSE}
library(stabilityselectr)
```


## Help

```{r help, eval = FALSE}
library(help = stabilityselectr)
```


## Package Notes

* The `stabilityselectr` package is easy to use.
* It is my first go-to when looking at dimensionality reduction
  and upstream feature selection.

