---
output: github_document
---


<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
cvr <- covr::percent_coverage(covr::package_coverage())
coverage <- sprintf(
  "https://img.shields.io/badge/coverage-%0.1f%%25-%s.svg?style=flat&logo=codecov",
  cvr, ifelse(cvr > 75, "success", ifelse(cvr > 50, "yellow", "critical"))
)
#lints <- length(lintr::lint_dir("R", show_progress = FALSE))
lints <- 0
lintage <- sprintf(
  "https://img.shields.io/badge/lints-%s-%s.svg?style=flat&logo=gitlab",
  lints, ifelse(lints < 25, "success", ifelse(lints < 50, "yellow", "critical"))
)
```


# The `stabilityselectr` package

<!-- badges: start -->
[![build](https://img.shields.io/badge/build-passing-success.svg?logo=travis)](http://bitbucket.sladmin.com/projects/SV/repos/somastabilityselection/commits)
![coverage](`r coverage`)
![lint](`r lintage`)
[![pkgdown](https://img.shields.io/badge/pkgdown-_-critical.svg?logo=semantic-web&logoColor=red)](https://bitbucket.sladmin.com/pages/SV/somastabilityselection/bb-pkgdown/browse/index.html)
[![License: GPL-3](https://img.shields.io/badge/License-GPL3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
<!-- badges: end -->




## Overview

The `stabilityselectr` package performs stability selection with a 
variety of kernels provided by the `glmnet` package, and provides 
simple tools for plotting and extracting selected features.
There is additional functionality designed to facilitate
various forms of permutation clustering analyses.


For cross-referenced help, running examples, and vignettes, please visit the 
[pkgdown](https://bitbucket.sladmin.com/pages/SV/somastabilityselection/bb-pkgdown/browse/index.html)
website.


----------------


## Custom Installation

It is possible to install a specific version of `stabilityselectr` 
(i.e. one differing from your current installation of 
[SLIDE](http://bitbucket.sladmin.com/projects/BFX/repos/slide/browse)),
but it comes with a possible trade-off in the reproducibility of your work! 


```{r install-git, eval = FALSE}
remotes::install_github("stabilityselectr")
```


----------------


## Usage

To load `stabilityselectr` simply make a call to `library()` as usual:

```{r, eval = FALSE}
library(stabilityselectr)
```


## Help summary of the package

```{r help, eval = FALSE}
library(help = stabilityselectr)
```


## Notes about the package

* The `stabilityselectr` package is easy to use.
* There is some cool stuff we can do.



-----------------


#### LICENSE

