---
title: "Progeny and Stability Clustering"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Progeny and Stability Clustering}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
library(stabilityselectr)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>"
)
```


## Useful functions:

* `progeny_cluster()`: performs progeny clustering
* `plot()` and `print()`: S3 methods for class `pclust`
* `stability_cluster()`: performs stability clustering


--------------


## Progeny Clustering via `progeny_cluster()`

Select the optimal number for clustering using Progeny Clustering.
The "true" number of clusters in the `progeny_data` object is 3.



```{r progeny}
pc <- progeny_cluster(progeny_data, clust_iter = 2:9L,
                      repeats = 10L, n_iter = 25L, size = 6)
pc
```

```{r plot-pclust, fig.height = 4.5, fig.width = 9}
plot(pc)
```


-------------


## Stability Clustering via `stability_cluster()`

Partitioning Around Medoids (PAM) is used both because
is uses a more robust measurement of the cluster centers (medoids) and
because this implementation keeps the cluster labels consistent across
runs, a key feature in calculating the across run stability. This does
not occur using `stats::kmeans()` where the initial cluster
labels are arbitrarily assigned.

True clusters are:

* cluster 1 -> samples `1:50`
* cluster 2 -> samples `51:100`
* cluster 3 -> samples `101:150`


```{r stab-clusters}
stab_clust <- stability_cluster(progeny_data, k = 3L, n_iter = 750L,
                                r_seed = 999) |>
  dplyr::mutate(true_cluster = rep(1:3L, each = 50L))

# 3-way confusion matrix
stab_clust |>
  with(table(truth = true_cluster, predicted = prob_k))

# view incorrect clusters
stab_clust |>
  dplyr::filter(true_cluster != prob_k)
```


### Plotting Clusters

We can plot the original `progeny_data` object, which has 3 true
clusters, and identify which samples that were "incorrectly"
clustered via stability clustering with an outline of the 
incorrect color.

```{r plot-clusters, fig.height = 4, fig.width = 9.5, echo = FALSE}
# identify false clusters
cols <- c("#24135F", "#00A499", "#840B55")
withr::with_par(list(mgp = c(2.00, 0.75, 0.0), bg = "white",
                     mar = c(3, 4, 3, 1), mfrow = 1:2L), {
  plot(progeny_data,
       col = cols[stab_clust$true_cluster],
       bg  = cols[stab_clust$true_cluster],
       pch  = stab_clust$true_cluster + 20, lwd = 1, cex = 1.75,
       main = "Orig. Simulated 3 Cluster Data")
  plot(progeny_data,
       col = cols[stab_clust$prob_k],
       bg  = cols[stab_clust$true_cluster],
       pch = stab_clust$true_cluster + 20, lwd = 2.5, cex = 1.5,
       main = "Predicted Clusters via Stability Clustering")
})
```


-------------

## References

Hu, C.W., Kornblau, S.M., Slater, J.H. and A.A. Qutub (2015).
Progeny Clustering: A Method to Identify Biological Phenotypes. Scientific Reports,
5:12894. http://www.nature.com/articles/srep12894

