---
title: "Progeny and Stability Clustering"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Progeny and Stability Clustering}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(stabilityselectr)
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>"
)
set.seed(101)
```


## Useful functions:

* `progenyCluster()`: performs progeny clustering
* `plot()`: S3 plot method for class `pclust`
* `stabilityCluster()`: performs stability clustering


--------------


## Progeny Clustering via `progenyCluster()`

Select the optimal number for clustering using Progeny Clustering. The "true"
number of clusters in the `progeny_data` object is 3.



```{r progeny}
pc <- progenyCluster(progeny_data, clust.iter = 2:9, reps = 10, iter = 25, size = 6)
pc
```

```{r plot-pclust, fig.height = 4.5, fig.width = 9}
plot(pc)
```


-------------



## Stability Clustering via `stabilityCluster()`

Partitioning Around Medoids (PAM) is used both because
is uses a more robust measurement of the cluster centers (medoids) and
because this implementation keeps the cluster labels consistent across
runs, a key feature in calculating the across run stability. This does
not occur using `stats::kmeans()` where the initial cluster
labels are arbitrarily assigned.

Correct clusters are:

* cluster 1 -> samples 1:50
* cluster 2 -> samples 51:100
* cluster 3 -> samples 101:150

```{r stab-clusters}
set.seed(999)
stab_clust <- stabilityCluster(progeny_data, k = 3, iter = 500)
stab_clust

# view 3-way confusion matrix
table(actual = rep(1:3, each = 50), predicted = stab_clust$ProbK)

# identify false clusters
stab_clust <- stab_clust |>
  dplyr::mutate(
    sample = dplyr::row_number(),
    pch    = rep(16:18, each = 50),
    pch    = dplyr::case_when(
      sample <= 50 & ProbK != 1L ~ 13L,                 # cluster 1
      sample > 50 & sample <= 100 & ProbK != 2L ~ 13L,  # cluster 2
      sample > 100 & ProbK != 3L ~ 13L,                 # cluster 3
      TRUE ~ pch
    )
  )

# view incorrect clusters (n = 6)
stab_clust |> dplyr::filter(pch == 13)
```


### Plotting Clusters

We can plot the `progeny_data` object, which has 3 main clusters, and identify
which samples that were "correctly" clustered via stability clustering with
an "X".

```{r plot-clusters, fig.height = 4.5, fig.width = 9}
par.def <- list(mgp = c(2, 0.75, 0), mar = c(3, 4, 3, 1))
par(par.def)
par(mfrow = 1:2)
plot(progeny_data, col = rep(2:4, each = 50),
     pch = rep(16:18, each = 50), cex = 1.75, main = "Simulated 3 Cluster Data")
plot(progeny_data, col = rep(2:4, each = 50), pch = stab_clust$pch, cex = 1.75,
     main = "Stability Clustering")
```


-------------------

## References
Hu, C.W., Kornblau, S.M., Slater, J.H. and A.A. Qutub (2015).
Progeny Clustering: A Method to Identify Biological Phenotypes. Scientific Reports,
5:12894. http://www.nature.com/articles/srep12894
