---
title: "Introduction to Stability Selection"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to Stability Selection}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(stabilityselectr)
library(ggplot2)
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>"
)
```


The `stabilityselectr` package performs stability
selection with a variety of kernels provided by
the `glmnet` package, and provides simple tools
for plotting and extracting selected features.
There is additional functionality designed to facilitate
various forms of permutation clustering analyses.


---------------


## Useful functions in `stabilityselectr`

* `stability_selection()`
* `is_stab_sel()`
* `get_stable_features()`
* `calc_emp_fdr()`
* `calc_emp_fdr_breaks()`
* `plot_emp_fdr()`
* `plot_permuted_data()`
* `progeny_cluster()`
* `stability_cluster()`


---------------

## Examples

A typical stability selection analysis might be similar to the one below.

#### Run `stability_selection()`
```{r stab-sel}
set.seed(101)
n_feat      <- 20L
n_samples   <- 100L
x           <- matrix(rnorm(n_feat * n_samples), n_samples, n_feat)
colnames(x) <- paste0("feat", "_", head(letters, n_feat))
y           <- sample(1:2, n_samples, replace = TRUE)
stab_sel    <- stability_selection(x, y, "binomial", n_iter = 500L)
is_stab_sel(stab_sel)
stab_sel
```

#### Plot stability paths

```{r plot-stab-sel, fig.width = 8, fig.height = 6}
plot(stab_sel, thresh = 0.85)
```


#### Stable Features at a threshold

```{r get-features}
get_stable_features(stab_sel, thresh = 0.85)

# at multiple thresholds
get_stable_features(stab_sel, thresh = seq(0.7, 0.9, 0.05))
```

---------------

## Progeny and Stability Clustering

See separate vignette on clustering: `vignette("progeny-clustering")`.


---------------

## References

Meinshausen, N and P Buhlmann. (2010). Stability selection.
Journal of the Royal Statistical Society: Series B (Statistical
Methodology), **72**: 417-473. doi: 10.1111/j.1467-9868.2010.00740.x
